Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2013-12-25 paper.tex
More blockchain :)

The blockchain is Bitcoin's main innovation. Blockchains are data-structures that were invented specifically for the Bitcoin project but they can be applied anywhere a distributed consensus needs to be established in the presence of malicious or untrustworthy actors.

Let's say Alice wants to send money to Bob. Bitcoin addresses are hash
\begin{center}
Key-Hash = RIPEMD-160(SHA-256(public key))
$\text{BTC}_{\text{Address}}$ = Base58(Version +\footnote{The + sign is a string concatenation} Key-Hash + Checksum)
\end{center}
In Bitcoin, the blockchain is used to log all of the transactions. But how does the blockchain work? What prevents anyone to append malicious entries at the bottom of the blockchain.

>>>>

The blockchain is Bitcoin's main innovation. Blockchains are data-structures that were invented specifically for the Bitcoin project to store the history of all past transactions but they can be applied anywhere a distributed consensus needs to be established in the presence of malicious or untrustworthy actors.

To understand how they work, let's take an example and see what happens when Alice tries to transfer money to Bob. Every user on the network has one address. Bitcoin addresses are generated based a public key. 
\begin{center}
Key-Hash = RIPEMD-160(SHA-256(public key))
$\text{BTC}_{\text{Address}}$ = Base58(Version +\footnote{The + sign is a string concatenation} Key-Hash + Checksum)
\end{center}

Private-public keypairs are generated when making new Bitcoin addresses. The curved used in Bitcoin is secp256k1 which is surprisingly a NIST recommended curve.\cite{VOID}

Alice must know Bob's address to send him money. Now that Alice has Bob's address, she creates a new message saying she sends a few Bitcoins to Bob and uses her private key to generate an ECDSA signature. Once she has generated that message and signed it, she starts gossiping about her transaction on the network, her peers hear about the transaction, they verify if Alice has enough money to make the transaction and verify the signature, if the transaction looks legitimate, they start telling all of their peers. Peers that are miners, eventually hear about this transaction and it's added to the transactions memory pool. This pool is a queue of transactions that are not yet merged in the blockchain. But now how can we merge transactions into the blockchain?
